An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-07-01 EconGrowth.Rnw
Not evaluating any R code except for the triangle plots.

<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.">>=
cdeResampleTrianglePlot(energyType="Q")
@

>>>>

<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.", eval=TRUE>>=
cdeResampleTrianglePlot(energyType="Q")
@
